Co-methylation

### 2015-09-28 Rmarkdown/comethylation.Rmd
Closes #26

In summary, the correlations of pairs of $\beta$-values should be cautiously interpreted, bearing in mind that these are somewhat crude summaries that hide many details of the underyling scatterplots.

@@

\FloatBarrier
\subsection{Results}

@@

\subsubsection{Can we collapse by strand?}

Figures \ref{fig:EPISCOPE_spearman_beta_cors_min_cov_5}, \ref{fig:Lister_spearman_beta_cors_min_cov_5}, \ref{fig:Seisenberger_spearman_beta_cors_min_cov_5} and \ref{fig:Ziller_spearman_beta_cors_min_cov_5} show the Spearman correlations of $\beta$-values for $NIL = 0$ pairs of CpGs stratified by strand. Since the trend in the correlations are very similar for the two strands, I decided to use the strand-collapsed $\beta$-values in all that follows.

>>>>

In summary, the correlations of pairs of $\beta$-values should be cautiously interpreted, bearing in mind that these are somewhat crude summaries that hide many details of the underlying scatterplots.

@@

\FloatBarrier
\subsection{Results}\label{sec:results-correlation-of-methylation-levels}

@@

\subsubsection{The effect of strand}

We have seen that the CpG $\beta$-values are very highly correlated across strands for most samples when the minimum sequencing coverage is at least $5\times$ ($r = 0.8$ to $0.9$, Section \ref{sec:empirical-distributions-of-beta-values}). While there are some notable exceptions (the embryo-derived and embryonic stem cell samples), I have opted to collapse by strand in most of the analyses in Section \ref{sec:results-correlation-of-methylation-levels} in order to simplify the plots.

Figures \ref{fig:EPISCOPE_spearman_beta_cors_min_cov_5}, \ref{fig:Lister_spearman_beta_cors_min_cov_5}, \ref{fig:Seisenberger_spearman_beta_cors_min_cov_5} and \ref{fig:Ziller_spearman_beta_cors_min_cov_5} are the only plots to stratify by strand and show the Spearman correlations of $\beta$-values for $NIL = 0$ pairs of CpGs. These correlations are very similar across strands, even for those embyro-derived and embryonic stem cell samples.
